---
title: "Simple document"
author: Ifrah
date: 2021-09-16
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(readxl)
library(haven)
```

# Import Data

I want to import 'FAS_litters.csv'.

```{r}
litters_df = read.csv("data/FAS_litters.csv")
```

```{r}
names(litters_df)

litters_df = janitor::clean_names(litters_df)
```

# Displaying 20 rows from the start and 10 from the end in litters_df

```{r}
head(litters_df, 20)
tail(litters_df, 10)
```

```{r}
skimr::skim(litters_df)
```

## Arguments in read_csv

```{r}
litters_df =
  read_csv(
    "data/FAS_litters.csv",
    skip = 5,
    col_names = FALSE,
    na = "Low8"
  )
```


```{r}
litters_df = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
tail(litters_df)
```

## Reading MLB data xlsx file.

```{r}
mlb11_df = read_excel("data/mlb11.xlsx")
```

## LotR words file.

```{r}
fellow_df = read_excel("data/LotR_Words.xlsx", range = "B3:D6")
```

## Read SAS File

Tried reading SAS file but got errors.

```{r, eval = FALSE}
pulse_df = read_sas("data/public_pulse_data.sas7bdat")
````

## why to never use read.csv instead of read_csv

read.csv will read everything as a dataframe. read_csv will read things as a tibble.

```{r}
litters_df_base = read.csv("data/FAS_litters.csv")
```

## How do I export data?

```{r}
write_csv(fellow_df, "data/fellowship_words.csv")
```






